Reproduction of \"Who Does Voter ID Keep from Voting?\" by Bernard L. Fraga and Michael G. Miller (2022)

### 2024-02-13 paper/SSRP/reproduction_paper.qmd
Added county boundaries data, updated script for downloading data, and reproduction paper

#### Load data ####
cleaned_reason_data <- read_csv("../../data/analysis_data/cleaned_reason_data.csv", show_col_types = FALSE)
```
# Introduction
This report contains the figures replicated from Bernard L. Fraga and Michael G. Miller's paper, "Who Does Voter ID Keep from Voting?" [@citeVoterIDPaper]. In our replication, the statistical programming language, R [@citeR], `dataverse` [@citedataverse], `tidyverse` [@citetidyverse], `ggplot2` [@citeggplot2], `haven` [@citehaven], `readr` [@citereadr], and `knitr` [@citeknitr] were used to retrieve, clean, and analyze the datasets to create the figures and tables.

>>>>

#### Load data ####
cleaned_reason_data <- read_csv("../../data/analysis_data/cleaned_reason_data.csv", show_col_types = FALSE)
```
# Introduction
This report contains the figures replicated from Bernard L. Fraga and Michael G. Miller's paper, "Who Does Voter ID Keep from Voting?" [@citeVoterIDPaper]. In our replication, the statistical programming language, R [@citeR], `dataverse` [@citedataverse], `tidyverse` [@citetidyverse], `ggplot2` [@citeggplot2], `haven` [@citehaven], `readr` [@citereadr], `janitor` [@citejanitor], and `knitr` [@citeknitr] were used to retrieve, clean, and analyze the datasets to create the figures and tables.
